Supporting Information: Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-21 paper/current/supp.tex
revert refernece part

%
% Figure - gravity correlation
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
		\textbf{a.}
		Embedding distance explains more flux than geographic distance (\textbf{b}).
		Red line is the line of best fit.
		Black dots are mean flux across binned distances.
		Color of each hex bin indicates frequency of organization pairs.
		Results here are identical to those shown in Fig.2.
		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
		\textbf{e-f.} embedding distance is more robust than geographic distance when considering only across-country organization pairs.
	}
	\label{fig:supp:gravity_correlation}
\end{figure}

%
% Figure - gravity predictions based on subset or global
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
	\caption{
		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
		a perfect prediction yields all points on the black line.
		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.2e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
		this is the same data as shown in Fig.2f and Fig.2h.
	}
	\label{fig:supp:gravity_prediction_subsets}
\end{figure}

>>>>

%
% Figure - gravity correlation
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
		\textbf{a.}
		Embedding distance explains more flux than geographic distance (\textbf{b}).
		Red line is the line of best fit.
		Black dots are mean flux across binned distances.
		Color of each hex bin indicates frequency of organization pairs.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
		\textbf{e-f.} embedding distance is more robust than geographic distance when considering only across-country organization pairs.
	}
	\label{fig:supp:gravity_correlation}
\end{figure}

%
% Figure - gravity predictions based on subset or global
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
	\caption{
		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
		a perfect prediction yields all points on the black line.
		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
	}
	\label{fig:supp:gravity_prediction_subsets}
\end{figure}
